Supermassive black hole and host bulge affairs \\ I. True to life galaxy decomposition.

### 2015-05-27 papers/data_paper/datapaper.tex
stancaaa

  individual galaxies \\

@@

  IC 1459 is an elliptical galaxy with a fast counterrotating stellar component \citep{franxillingworth1988ic1459,cappellari2002ic1459},
  nuclear dust and an indication of a central stellar disk \citep{forbes1994ic1459}.
  The kinematically decoupled component cannot be identified as a separate structure in photometric observations.
  This galaxy has also an unresolved partially depleted core \citep{rusli2013}. \\ % ($R_{\rm break} = 0''.69$, \citealt{rusli2013}).

  \emph{1D fit -- }
  Our isophotal analysis confirms a simple morphology for IC 1459, with no evident embedded components.
  We masked the innermost $6''.1$ affected by the partially depleted core 
  and we fit this galaxy with a S\'ersic profile. \\

  \emph{Other models -- } 
  The best-fit model of L+14 is in reasonable agreement with our results. 
  S+11 obtained the smallest S\'ersic index because they fit a nuclear component rather than masking the core. 
  R+13 obtained the smallest effective radius 
  because they fit a circularized light profile that only extends out to $R_{\rm eq} \lesssim 60''$.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/ic1459_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for IC 1459.}
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of IC 1459.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + m-c & $63.1$  &  $6.6$ \\
  T.W. 1D eq.  & S-bul + m-c & $57.3$  &  $7.0$ \\
  T.W. 2D      & S-bul + m-c & $87.5$  &  $8.3$ \\
  \hline
  S+11         & S-bul + G-n   & $61.1$  &  $6.0$ \\
  R+13         & core-S\'ersic & $45.4$  &  $7.6$ \\
  L+14         & S-bul + m-c   & $62.4$  &  $8.3$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:ic1459}
  \end{table}

@@

  IC 2560 is a barred spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}
  and dust within the central $2''.5$ \citep{martini2003}.\\

  \emph{1D fit -- }
  A visual inspection of the image of IC 2560 reveals a boxy bulge and
  a large scale bar that extends out to $R_{\rm maj} \lesssim 43''$.
  The disk appears to be slightly lopsided along the direction of the bar,
  due to two non-symmetric ansae, but it becomes symmetric beyond $R_{\rm maj} \gtrsim 60''$. 
  This is why the surface brightness profile deviates from a perfect exponential
  in the radial range $42'' \lesssim R_{\rm maj} \lesssim 60''$, which has been excluded from the fit.
  Motivated by the presence of a strong optical AGN and dust in the nucleus, 
  we accounted for an excess of non-stellar light by adding a central Gaussian component to the model.\\

  \emph{Other models -- } 
  In their model, S+11 did not account for the bar component and thus overestimated the effective radius and the S\'ersic index of the bulge.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/ic2560_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for IC 2560.}
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of IC 2560.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-d + F-bar + G-n & $6.1$  &  $0.8$ \\
  T.W. 1D eq.  & S-bul + e-d + F-bar + G-n & $4.5$  &  $0.6$ \\
  \hline
  S+11         & S-bul + e-d + G-n & $27.5$  &  $2.0$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:ic2560}
  \end{table}

@@

  IC 4296 is an elliptical galaxy. 
  Due to its high stellar velocity dispersion, this galaxy is expected to host a partially depleted core.

  \emph{1D fit -- }
  After masking the innermost $6''.1$, 
  we found that a single S\'ersic profile provides a fairly good description of this galaxy.

  \emph{Other models -- } 
  S+11 obtained the smallest effective radius and S\'ersic index because they fit a nuclear component rather than masking the core. 
  L+14 obtained the largest effective radius and S\'ersic index, 
  although the 1D representation of their 2D fit (their Figure 8) shows that their model overestimates the galaxy light at large radii ($R > 100''$), 
  implying the need for a smaller $R_{\rm e}$ and $n$. 
  We did not find any conclusing explanation for this, 
  but we suspect it may be due to the different pixel weighting scheme that they used.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/ic4296_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for IC 4296.}
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of IC 4296.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + m-c & $65.9$  &  $5.8$ \\
  T.W. 1D eq.  & S-bul + m-c & $68.1$  &  $6.2$ \\
  T.W. 2D      & S-bul + m-c & $82.3$  &  $6.6$ \\
  \hline
  S+11         & S-bul + G-n & $33.6$  &  $4.0$ \\
  L+14         & S-bul + m-c & $97.8$  &  $8.2$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:ic4296}
  \end{table}

@@

  M31, the Andromeda galaxy, is a spiral galaxy. 
  Although for decades this galaxy had been classified as an unbarred spiral,
  recent works have unraveled the presence of a bar \citep{athanassoulabeaton2006m31,beaton2007m31,morrison2011m31}.
  M31 also features a ring-like structure at $R_{\rm maj} \sim 50'$ \citep{athanassoulabeaton2006m31}.

  \emph{1D fit -- }
  We applied the \emph{smoothing} technique described in Section \ref{sec:smooth} to the analysis of M31.
  The region $2000'' \lesssim R_{\rm maj} \lesssim 3400''$, where the pseudo-ring is observed, was excluded from the fit.
  A S\'ersic + exponential fit is not adequate to describe the light profile of M31,
  as the residuals of such fit display a structure in correspondence of the bar ($R_{\rm maj} \lesssim 1500''$).
  The addition of a Ferrer function to account for the bar notably improved the fit.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m31_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M31.}
  \end{center}
  \end{figure}

@@

  M49, the brightest member of the Virgo cluster, is a giant elliptical galaxy 
  with a slightly resolved partially depleted core \citep{rusli2013}. \\ %($R_{\rm break} = 1''.8$, \citealt{rusli2013}).

  \emph{1D fit -- }
  We excluded from the fit the innermost $12''$.
  We found no evidence for embedded components and
  we fit M49 with a single S\'ersic profile. \\

  \emph{Other models -- } 
  The effective radius estimated by R+13 is larger than that measured by us along the equivalent axis.
  Since their circularized light profile is almost 3 times more extended than ours, 
  it is possible that their best-fit model required a larger $R_{\rm e}$ to account for the galaxy intracluster halo light.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m49_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M49.}
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of M49.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + m-c   & $190.2$  &  $6.6$ \\
  T.W. 1D eq.  & S-bul + m-c   & $135.3$  &  $5.4$ \\
  T.W. 2D      & S-bul + m-c   & $151.9$  &  $5.5$ \\
  \hline
  R+13         & core-S\'ersic & $199.0$  &  $5.6$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:m49}
  \end{table}

@@

  M59 is an elliptical galaxy with an edge-on, intermediate-scale embedded disk \citep{scorzabender1995}
  and a thin, faint nuclear stellar disk \citep{ferrarese2006acsvcs,ledo2010}.\\

  \emph{1D fit -- }
  The intermediate-scale embedded disk is clearly visible in our unsharp mask image, and 
  the velocity field confirms the presence of a rapidly rotating component. 
  This has been modeled with an exponential function.
  We chose not to account for the nuclear stellar disk by excluding the innermost $6''.1$ from the fit. \\

  \emph{Other models -- } 
  We observed no significant discrepancies between our results and the best-fit models of S+11 and V+12.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M59.}
  \end{center}
  \end{figure}

@@

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%\clearpage\newpage\noindent
  %%
  %%{\bf M60 -- NGC 4649 \\}
  %%
  %%exclude it, doesn't make sense
  %%
  %%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \clearpage\newpage\noindent
  {\bf M64 -- NGC 4826 \\}

  M64 is a dusty spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}. \\

  \emph{1D fit -- }
  A large-scale bar ($R_{\rm maj} \lesssim 50''$) can be identified in the unsharp mask 
  and produces corresponding peaks in the ellipticity, PA and B4 profiles.
  We modeled it with a Ferrer function.
  Additional peaks in the ellipticity, PA and B4 profiles at $R_{\rm maj} \sim 15''$ 
  signal the presence of an embedded disky component, that we described with a low-$n$
  S\'ersic function.
  Although the galaxy is dusty and hosts an AGN, we do not observe any nuclear excess of light 
  in the fit residuals and therefore we consider unnecessary to add a nuclear component to our model. \\

  \emph{Other models -- } 
  The best-fit model of B+12 is in reasonable agreement with our results.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m64_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M64.}
  \end{center}
  \end{figure}

@@

  M81 is an early-type spiral galaxy.
  This galaxy features two bars \citep{elmegreen1995m81,gutierrez2011,erwindebattista2013}. \\

  \emph{1D fit -- }
  We applied the \emph{smoothing} technique described in Section \ref{sec:smooth} to the analysis of M81.
  The bars are not particularly evident in the galaxy image or in the unsharp mask.
  Any attempt to account for the bars in the fit was unsuccessful. 
  For this reason, we used a simple S\'ersic + exponential model to describe M81. \\

  \emph{Other models -- } 
  GD07 and B+12 obtained estimates of the effective radius larger than ours by a factor of two. 
  This is not particularly surprising, given the complicated surface brightness distribution of this galaxy. 
  The large measurement of the effective radius reported by S+11 is the most discrepant, 
  but the reasons for this are unclear.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m81_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M81.}
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of M81.}
  \begin{center}
  \begin{tabular}{llccc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-d  & $31.0$  &  $1.7$ \\
  T.W. 1D eq.  & S-bul + e-d  & $33.2$  &  $2.1$ \\
  %T.W. 2D	&   & $$  & $$  &  $$ \\
  \hline
  GD07      & S-bul + e-d	 & $68.1$   &  $3.3$ \\
  S+11      & S-bul + e-d + G-n  & $127.3$  &  $3.0$ \\
  B+12      & S-bul + e-d	 & $50.0$   &  $2.6$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:m81}
  \end{table}

@@

  M84 is an elliptical galaxy with a slightly resolved partially depleted core \citep{rusli2013}.\\ %($R_{\rm break} = 1''.5$, \citealt{rusli2013}).

  \emph{1D fit -- }
  The unsharp mask reveals a faint inner component ($R_{\rm maj} \lesssim 12''$). 
  Here we excluded the data within $R_{\rm maj} < 13''.8$ and modeled the galaxy with a S\'ersic profile.\\

  \emph{Other models -- } 
  The results obtained by S+11, R+13 and L+14 are in good agreement with those obtained by us. 
  B+12 did not mask the core and thus underestimated the effective radius and the S\'ersic index. 
  V+12 used the same model as R+13, L+14 and us, 
  but the smaller radial extent of their data led them to underestimate the effective radius and the S\'ersic index.
  It is not clear why GD07 obtained smaller estimates of the effective radius and the S\'ersic index, 
  since they tipically did not fit the innermost data points of their light profiles.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m84_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M84.}
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of M84.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + m-c   & $101.6$  &  $7.8$ \\
  T.W. 1D eq.  & S-bul + m-c   & $129.8$  &  $7.9$ \\
  T.W. 2D      & S-bul + m-c   & $181.8$  &  $8.4$ \\
  \hline
  GD07         & S-bul         & $75.1$   &  $5.6$ \\
  S+11         & S-bul + G-n   & $105.9$  &  $7.0$ \\
  V+12         & S-bul + m-c   & $28.7$   &  $3.5$ \\
  B+12         & S-bul         & $63.6$   &  $4.1$ \\
  R+13         & core-S\'ersic & $126.2$  &  $7.1$ \\
  L+14         & S-bul + m-c   & $139.0$  &  $8.3$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:m84}
  \end{table}

@@

  M87 is a giant elliptical galaxy belonging to the Virgo cluster.
  This galaxy has a large ($> 7''$), partially depleted core \citep{ferrarese2006acsvcs}.\\

>>>>

  individual galaxies \\
  For each galaxy, we show a figure and a table. 
  The figure illustrates our 1D best-fit model and the galaxy isophotal parameters. 
  The left panels refer to the major-axis $R_{\rm maj}$, 
  while the right panels refer to the equivalent-axis $R_{\rm eq}$, 
  i.e.~the geometric mean of the major ($a$) and minor ($b$) axis ($R_{\rm eq} = \sqrt{ab}$).
  The top panels display the galaxy surface brightness ($\mu$) radial profiles obtained with a linear sampling. 
  The black points are the observed data.  
  The color lines represent the individual (PSF-convolved) model components:
  red=S\'ersic, dark blue=exponential, green=Gaussian, cyan=Ferrer, gray=Gaussian ring, pink=PSF. 
  The best-fit parameters for the S\'ersic bulge model are inset.
  The total (PSF-convolved) model is shown with a black dashed line. 
  The residual profile ($data - model$) is shown as $\Delta \mu$ in the second row.
  The horizontal grey dashed line corresponds to an intensity 
  equal to three times the root mean square of the sky background fluctuations ($3 \times RMS_{\rm sky}$).
  $\Delta$ denotes the rms scatter of the fit in units of $\rm mag~arcsec^{-2}$.
  The lower six panels show the ellipticity ($\epsilon$), position angle ($PA$) and fourth harmonic ($B4$) radial profiles. \\
  The table reports a comparison between our results (from both our 1D and 2D decompositions) and those obtained by the following authors: 
  GD07 = \citeauthor{grahamdriver2007} (\citeyear{grahamdriver2007}, who performed 1D fits along the major-axis), 
  L+10 = \citeauthor{laurikainen2010} (\citeyear{laurikainen2010}, who performed 2D fits), 
  S+11 = \citeauthor{sani2011} (\citeyear{sani2011}, who performed 2D fits), 
  B+12 = \citeauthor{beifiori2012} (\citeyear{beifiori2012}, who performed 2D fits), 
  V+12 = \citeauthor{vika2012} (\citeyear{vika2012}, who performed 2D fits), 
  R+13 = \citeauthor{rusli2013} (\citeyear{rusli2013}, who performed 1D fits along the equivalent-axis),
  and L+14 = \citeauthor{lasker2014data} (\citeyear{lasker2014data}, who performed 2D fits).
  Each galaxy model is the sum of its individual components, which are expressed with the following nomenclature: (analytic function)-(physical component).
  The analytic functions can be: S=S\'ersic, e=exponential, G=Gaussian, F=Ferrer, M=Moffat and PSF.
  The physical components can be: bul=bulge or spheroid, d=disk, id=inner disk, bar, n=nucleus, l=lens or oval, r=ring, halo and spiral arms. 
  When a nuclear component or a partially depleted core have been masked, we signal them as ``m-n'' and ``m-c'', respectively.
  For example, the model ``S-bul + e-d + e-id + m-n + G-r'' reads ``S\'ersic-bulge + exponential-disk + exponential-inner disk + mask-nucleus + Gaussian-ring''. 
  The core-S\'ersic model used by \cite{rusli2013} is always implicitly associated with the galaxy spheroidal component. 
  When fitting their galaxy light profiles, \citeauthor{grahamdriver2007} excluded the innermost data points. 
  Their models implicitly include ``m-n'' or ``m-c''. 
  In the table caption, we comment on the most significant discrepancies between our results and those obtained by the other studies.

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/ic1459_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for IC 1459.
  IC 1459 is an elliptical galaxy with a fast counterrotating stellar component \citep{franxillingworth1988ic1459,cappellari2002ic1459},
  nuclear dust and an indication of a central stellar disk \citep{forbes1994ic1459}.
  The kinematically decoupled component cannot be identified as a separate structure in photometric observations.
  This galaxy has also an unresolved partially depleted core \citep{rusli2013}.  % ($R_{\rm break} = 0''.69$, \citealt{rusli2013}).
  Our isophotal analysis confirms a simple morphology for IC 1459, with no evident embedded components.
  After masking the innermost $6''.1$, we fit this galaxy with a S\'ersic profile.  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of IC 1459.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + m-c & $63.1$  &  $6.6$ \\
  T.W. 1D eq.  & S-bul + m-c & $57.3$  &  $7.0$ \\
  T.W. 2D      & S-bul + m-c & $87.5$  &  $8.3$ \\
  \hline
  S+11         & S-bul + G-n   & $61.1$  &  $6.0$ \\
  R+13         & core-S\'ersic & $45.4$  &  $7.6$ \\
  L+14         & S-bul + m-c   & $62.4$  &  $8.3$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:ic1459}
  \tablecomments{S+11 obtained the smallest estimate of the S\'ersic index because they fit a nuclear component rather than masking the core. 
  R+13 obtained the smallest estimate of the effective radius 
  because they fit a circularized light profile that only extends out to $R_{\rm eq} \lesssim 60''$. }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/ic2560_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for IC 2560. IC 2560 is a barred spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}
  and dust within the central $2''.5$ \citep{martini2003}.
  A visual inspection of the image of IC 2560 reveals a boxy bulge and
  a large scale bar that extends out to $R_{\rm maj} \lesssim 43''$.
  The disk appears to be slightly lopsided along the direction of the bar,
  due to two non-symmetric ansae, but it becomes symmetric beyond $R_{\rm maj} \gtrsim 60''$. 
  This is why the surface brightness profile deviates from a perfect exponential
  in the radial range $42'' \lesssim R_{\rm maj} \lesssim 60''$, which is excluded from the fit.
  Motivated by the presence of a strong optical AGN and dust in the nucleus, 
  we account for an excess of non-stellar light by adding a central Gaussian component to the model.}
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of IC 2560.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-d + F-bar + G-n & $6.1$  &  $0.8$ \\
  T.W. 1D eq.  & S-bul + e-d + F-bar + G-n & $4.5$  &  $0.6$ \\
  \hline
  S+11         & S-bul + e-d + G-n & $27.5$  &  $2.0$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:ic2560}
  \tablecomments{In their model, S+11 did not account for the bar component and thus overestimated the effective radius and the S\'ersic index of the bulge.}
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/ic4296_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for IC 4296.
  IC 4296 is an elliptical galaxy. 
  Due to its high stellar velocity dispersion, this galaxy is expected to host a partially depleted core. 
  After masking the innermost $6''.1$, 
  we find that a single S\'ersic profile provides a fairly good description of this galaxy.}
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of IC 4296.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + m-c & $65.9$  &  $5.8$ \\
  T.W. 1D eq.  & S-bul + m-c & $68.1$  &  $6.2$ \\
  T.W. 2D      & S-bul + m-c & $82.3$  &  $6.6$ \\
  \hline
  S+11         & S-bul + G-n & $33.6$  &  $4.0$ \\
  L+14         & S-bul + m-c & $97.8$  &  $8.2$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:ic4296}
  \tablecomments{
  S+11 obtained the smallest effective radius and S\'ersic index because they fit a nuclear component rather than masking the core. 
  L+14 obtained the largest effective radius and S\'ersic index, 
  although the 1D representation of their 2D fit (their Figure 8) shows that their model overestimates the galaxy light at large radii ($R_{\rm maj} > 100''$), 
  implying the need for a smaller $R_{\rm e}$ and $n$. 
  We suspect that this could be due to the pixel weighting scheme that they used.
  }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m31_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M31.
  M31, the Andromeda galaxy, is a spiral galaxy. 
  Although for decades this galaxy had been classified as an unbarred spiral,
  recent works have unraveled the presence of a bar \citep{athanassoulabeaton2006m31,beaton2007m31,morrison2011m31}.
  M31 also features a ring-like structure at $R_{\rm maj} \sim 50'$ \citep{athanassoulabeaton2006m31}. 
  We applied the \emph{smoothing} technique described in Section \ref{sec:smooth} to the analysis of M31.
  The region $2000'' \lesssim R_{\rm maj} \lesssim 3400''$, where the pseudo-ring is observed, is excluded from the fit.
  A S\'ersic + exponential fit is not adequate to describe the light profile of M31,
  as the residuals of such fit display a structure in correspondence of the bar ($R_{\rm maj} \lesssim 1500''$).
  The addition of a Ferrer function to account for the bar notably improves the fit.
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m49_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M49.
  M49, the brightest member of the Virgo cluster, is a giant elliptical galaxy 
  with a slightly resolved partially depleted core \citep{rusli2013}.  %($R_{\rm break} = 1''.8$, \citealt{rusli2013}).
  The data within the innermost $12''$ are excluded from the fit.
  We fit M49 with a single S\'ersic profile. 
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of M49.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + m-c   & $190.2$  &  $6.6$ \\
  T.W. 1D eq.  & S-bul + m-c   & $135.3$  &  $5.4$ \\
  T.W. 2D      & S-bul + m-c   & $151.9$  &  $5.5$ \\
  \hline
  R+13         & core-S\'ersic & $199.0$  &  $5.6$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:m49}
  \tablecomments{
  The equivalent-axis effective radius estimated by R+13 is larger than that measured by us.
  Since their circularized light profile is almost 3 times more extended than ours, 
  it is possible that their best-fit model required a larger $R_{\rm e}$ to account for the galaxy intracluster halo light.
  }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M59.
  M59 is an elliptical galaxy with an edge-on, intermediate-scale embedded disk \citep{scorzabender1995}
  and a thin, faint nuclear stellar disk \citep{ferrarese2006acsvcs,ledo2010}. 
  The intermediate-scale embedded disk is clearly visible in our unsharp mask image, and 
  the velocity map confirms the presence of a rapidly rotating component, which is modeled with an exponential function.
  We choose not to account for the nuclear stellar disk by excluding the innermost $6''.1$ from the fit.  
  }
  \end{center}
  \end{figure}

@@

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \clearpage\newpage\noindent
  {\bf M64 -- NGC 4826 \\}

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m64_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M64.
  M64 is a dusty spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}. 
  A large-scale bar ($R_{\rm maj} \lesssim 50''$) can be identified in the unsharp mask 
  and produces corresponding peaks in the ellipticity, PA and B4 profiles.
  This is modeled with a Ferrer function.
  Additional peaks in the ellipticity, PA and B4 profiles at $R_{\rm maj} \sim 15''$ 
  signal the presence of an embedded disky component, that we describe with a low-$n$ S\'ersic function.
  Although the galaxy is dusty and hosts an AGN, we do not observe any nuclear excess of light 
  in the fit residuals and therefore we consider unnecessary to add a nuclear component to our model. 
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m81_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M81.
  M81 is an early-type spiral galaxy.
  This galaxy features two bars \citep{elmegreen1995m81,gutierrez2011,erwindebattista2013}. 
  We applied the \emph{smoothing} technique described in Section \ref{sec:smooth} to the analysis of M81.
  The bars are not particularly evident in the galaxy image or in the unsharp mask.
  Any attempt to account for the bars in the fit was unsuccessful. 
  For this reason, we use a simple S\'ersic + exponential model. 
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of M81.}
  \begin{center}
  \begin{tabular}{llccc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-d  & $31.0$  &  $1.7$ \\
  T.W. 1D eq.  & S-bul + e-d  & $33.2$  &  $2.1$ \\
  %T.W. 2D	&   & $$  & $$  &  $$ \\
  \hline
  GD07      & S-bul + e-d	 & $68.1$   &  $3.3$ \\
  S+11      & S-bul + e-d + G-n  & $127.3$  &  $3.0$ \\
  B+12      & S-bul + e-d	 & $50.0$   &  $2.6$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:m81}
  \tablecomments{
  GD07 and B+12 obtained estimates of the effective radius larger than ours by a factor of two. 
  This is not particularly surprising, given the complicated surface brightness distribution of this galaxy. 
  The large measurement of the effective radius reported by S+11 is the most discrepant, 
  but the reasons for this are unclear. 
  }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m84_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M84.
  M84 is an elliptical galaxy with a slightly resolved partially depleted core \citep{rusli2013}. %($R_{\rm break} = 1''.5$, \citealt{rusli2013}). 
  The unsharp mask reveals a faint inner component ($R_{\rm maj} \lesssim 12''$). 
  We exclude the data within $R_{\rm maj} < 13''.8$ and model the galaxy with a S\'ersic profile.
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of M84.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + m-c   & $101.6$  &  $7.8$ \\
  T.W. 1D eq.  & S-bul + m-c   & $129.8$  &  $7.9$ \\
  T.W. 2D      & S-bul + m-c   & $181.8$  &  $8.4$ \\
  \hline
  GD07         & S-bul         & $75.1$   &  $5.6$ \\
  S+11         & S-bul + G-n   & $105.9$  &  $7.0$ \\
  V+12         & S-bul + m-c   & $28.7$   &  $3.5$ \\
  B+12         & S-bul         & $63.6$   &  $4.1$ \\
  R+13         & core-S\'ersic & $126.2$  &  $7.1$ \\
  L+14         & S-bul + m-c   & $139.0$  &  $8.3$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:m84}
  \tablecomments{
  B+12 did not mask the core and thus underestimated the effective radius and the S\'ersic index. 
  V+12 used the same model as R+13, L+14 and us, 
  but the smaller radial extent of their data led them to underestimate the effective radius and the S\'ersic index.
    }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m87_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M87.
  M87 is a giant elliptical galaxy belonging to the Virgo cluster.
  This galaxy has a large ($> 7''$), partially depleted core \citep{ferrarese2006acsvcs}.
  The morphology of M87 is similar to that of M49.
  The innermost $18''.5$ are excluded from the fit and
  a S\'ersic model is used to fit M87. 
  We note that the effective radius obtained from our 1D major-axis fit is more than a factor of two larger than that obtained from our 2D fit.
  This is due to the fact that the 2D model has fixed ellipticity and cannot account for the strong ellipticity gradient of the galaxy.  
  }
  \end{center}
  \end{figure}
